---
title: "vehicleVenn"
subtitle: "Household Ownership of Multiple Transport Vehicles in Uganda and Albania: Visualized With Quasi-proportional Venn Diagrams (nVennR)"
author: "Steven Bhardwaj"
date: "2021-08-08"
output: 
  html_document:
    theme:
      bootswatch: darkly
    code_folding: hide
---
<style type="text/css" media="screen, print">
.body {
  background-color: #000;
}
hr {
  background-color: #fff;
}
h1.title {
  padding-top: 2em;
  text-align: center;
}
h3.subtitle {
  text-align: center;
}
h4.author {
  font-size: 1em;
  text-align: center;
}
h4.date {
  font-size: 1em;
  text-align: center;
}
.center_plots {
  font-size: 1em;
  text-align: center;
  margin: auto;
  width: 60%;
}
.width_auto {
  width: auto;
}
#homeLink {
  font-size: 1.5em;
  color: #CCCCCC !important;
  opacity: 1;
  width: 5em;
	height: 1.2em;
  position: absolute;
  top: 3%;
  left: 50%;
  transform: translate(-50%, 0%);
}
.column {
  float: left;
  width: 50%;
}
/* Clear floats after the columns */
  .row:after {
    content: "";
    display: table;
    clear: both;
}
@media screen and (max-width: 1000px) {
  .column {
    width: 100%;
  }
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = TRUE)
```
```{r include=FALSE}
library(tidyverse)
library(readr)
library(nVennR)
library(magrittr)
library(haven)
library(slickR)
library(htmlwidgets)
library(htmltools)
source("./unofficial_libraries/iso_to_emoji.r")
#library(leaflet)

```

<!-- 
INKSCAPE COMMAND LINE CODE TO DO COLOR INVERSION OF THE SVG FILE
inkscape --with-gui ALB_2002.svg UGA_2011.svg UGA_2019.svg ALB_2005.svg UGA_2013.svg ALB_2012.svg UGA_2005.svg UGA_2015.svg UGA_2010.svg UGA_2018.svg --verb="EditSelectAll;org.inkscape.effect.filter.Invert.noprefs;FileSave;FileClose;FileQuit"
-->

<!-- LOGO / LINK TO HOME SCREEN -->
<div id="homeLink"><a href="../index.html"><p align="center">
bhrdwj.net
<br>
潘
</p></a></div>

<!-- MAIN BODY -->
### Abstract
The World Bank took very detailed surveys of representative samples of households in a bunch of countries. Uganda and Albania each had multiple years of data, so I downloaded those. I checked which families from the surveys had bicycles, motorbikes, or motor vehicles, and then made Venn Diagrams out of the results using nVennR in Rstudio.

<hr> ### Plots
- Sample is normalized to 1000 households in each graph.
    - So in each of these plots, more than half (500+/1000) of the sampled households had no vehicle in the household.
- Swipe the charts to compare different countries and years. Available are:
    - Albania `r iso_to_emoji_unicode("AL")``: 2002, 2005, 2012
    - Uganda `r iso_to_emoji_unicode("UG")`: 2010, 2011, 2013, 2015, 2018, 2019

<div class="center_plots">

``` {r}
#eval=FALSE, include=FALSE}
# what worked for editing some css inside the slider:
  # https://giters.com/yonicd/slickR/issues/58?amp=1
  # but still can't fix the background color haha

uri_df <- data.frame(
  country = c("AL", "AL", "AL", "UG", "UG", "UG", "UG", "UG", "UG"),
  year =    c( 2002, 2005, 2012, 2010, 2010, 2011, 2013, 2015, 2018),
  paths =  c("http://bhrdwj.net/r/svg/ALB_2002.svg", 
             "http://bhrdwj.net/r/svg/ALB_2005.svg", 
             "http://bhrdwj.net/r/svg/ALB_2012.svg",
             "http://bhrdwj.net/r/svg/UGA_2010.svg", 
             "http://bhrdwj.net/r/svg/UGA_2011.svg", 
             "http://bhrdwj.net/r/svg/UGA_2013.svg", 
             "http://bhrdwj.net/r/svg/UGA_2015.svg", 
             "http://bhrdwj.net/r/svg/UGA_2018.svg", 
             "http://bhrdwj.net/r/svg/UGA_2019.svg"
  )
) %>%
  mutate(flag = iso_to_emoji_unicode(country))

slickR_strings <- paste(uri_df$country, uri_df$flag, uri_df$year, sep=" ")

captions_dom <- slick_list(lapply(slickR_strings, function(x) 
  htmltools::tags$p(x,style = htmltools::css(color="#FFF", "background-color"='#000'))
  ))

slickR(obj = uri_df$paths, width = "100%", height = 400) %synch%
  ( slickR(obj = captions_dom, slideType = 'p') + settings(arrows = FALSE) )


```

``` {r echo=FALSE, results=TRUE}
#eval=FALSE
(slickR(obj = uri_df$paths, width = "100%", height=400) + settings(initialSlide = 4)) %synch%
  ( slickR(obj = captions_dom, slideType = 'p') + settings(arrows = FALSE, initialSlide = 4) )

```

<br>

</div>

<br>
<hr> 

### Discussion

I was particularly surprised at how many Albanian households didn't report owning any kind of vehicle in the survey. 🤔 

<hr>
## Code
### Import R Libraries
```{r eval=FALSE}
library(tidyverse)
library(readr)
library(nVennR)
library(magrittr)
library(haven)
library(slickR)
library(htmlwidgets)
library(htmltools)
source("./unofficial_libraries/iso_to_emoji.r")
```
<hr> ### Raw-data Pathnames
```{r}
#eval=FALSE}

# data source: 
# https://microdata.worldbank.org/index.php/catalog/lsms

# LOCAL PATHS
ALB_paths <- list(
  ALB_2002 = "./data/ALB_2002_LSMS_v01_M_STATA8/ndurables_cl.dta",
  ALB_2005 = "./data/ALB_2005_LSMS_v01_M_STATA8/dwellingC1_cl.dta",
  ALB_2012 = "./data/ALB_2012_from-gov-website_LSMS 2012_eng/Data_LSMS 2012/Modul_13C1_Household_Durables.sav"
)

UGA_paths <- list(
  UGA_2005 = "./data/UGA_2005_2009_UNPS_v01_M_Stata8/2009_GSEC14.dta",
  UGA_2010 = "./data/UGA_2010_UNPS_v01_M_Stata8/GSEC14.dta",
  UGA_2011 = "./data/UGA_2011_UNPS_v01_M_Stata/GSEC14.dta",
  UGA_2013 = "./data/UGA_2013_UNPS_v01_M_STATA8/GSEC14A.dta",
  UGA_2015 = "./data/UGA_2015_UNPS_v01_M_STATA8/gsec14.dta",
  UGA_2018 = "./data/UGA_2018_UNPS_v01_M_STATA12/hh/HH/GSEC14.dta",
  UGA_2019 = "./data/UGA_2019_UNPS_v01_M_STATA14/HH/gsec14.dta"
)
```
<hr> ### List of field-names for data cleaning
```{r}
#eval=FALSE}
ALB_vars <- list(
  ALB_2002 = list(item_names = "m3c_q01a", item_codes = "m3c_q01b" , num_owned = "m3c_q01c" ),
  ALB_2005 = list(item_names = "m13c1_q1a", item_codes = "m13c1_q1b" , num_owned = "m13c1_q1c"),
  ALB_2012 = list(item_names = "m13c1_q1a", item_codes = "m13c1_q1b", num_owned = "m13c1_q1c")
)
```
<hr> ### Data-cleaning for Albania data
```{r}
#eval=FALSE}
# Loop through the years for Albania
  # Each year, make a tidy data frame of household observations
df_list <- list()
for (key in names(ALB_paths)) {
  df_list[[{{key}}]] <- ALB_paths[[key]] %>%
    
    # MAKE COLUMN NAMES FROM DIFFERENT YEARS CONSISTENT
    {if (grepl(".sav", ALB_paths[[key]], fixed = TRUE)) read_sav(.) else
      if (grepl(".dta", ALB_paths[[key]], fixed = TRUE)) read_dta(.) else 
      print("bad data filepath")} %>%
    {if ("psu" %in% colnames(.)) mutate_at(., c("psu", "hh"), as.character) %>%
      mutate(hhid = paste(psu, "_", hh, sep=""), hh=NULL, psu=NULL) else .} %>%
    rename(names_ = ALB_vars[[{{key}}]]$item_names,
           codes_ = ALB_vars[[{{key}}]]$item_codes,
           num_   = ALB_vars[[{{key}}]]$num_owned) %>%
    
    # CLEAN AND SIMPLIFY COLUMNS
    select(hhid, names_, num_, codes_) %>%
    mutate(num_ = as.integer(num_))  %>%
    mutate(have_one = (num_ >= 1), num_ = NULL) %>%
    filter(names_ != "") %>%
    
    # TIDY BY WIDENING: ONE ROW FOR EACH HOUSEHOLD, ONE COLUMN FOR EACH ASSET TYPE
    pivot_wider(id_cols = c("hhid"), names_from=codes_, values_from = have_one) %>%
    
    # MAKE ASSET CODES HUMAN-READABLE.  COMBINE TRUCK AND CAR TO MOTOR VEHICLE.
    rename(bike = `120`, motorbike = `121`, car = `122`, truck = `123`) %>%
    mutate(motor_vehicle = car | truck, car=NULL, truck=NULL) %>%
    select(c("hhid", "bike", "motorbike", "motor_vehicle")) %>%
    mutate(country = (str_split(key, "_"))[[1]][[1]]) %>%
    mutate(year = (str_split(key, "_"))[[1]][[2]])
}
```
<hr> ### Data-cleaning for Uganda data
```{r}
#eval=FALSE}
# UGA
for (key in names(UGA_paths)) {
  df_list[[{{key}}]] <- UGA_paths[[key]] %>%
    read_dta() %T>%
    {colnames(.) <- tolower(colnames(.))} %T>%
    {colnames(.) <- sub("q0", "q", colnames(.))} %>%
    select(c("hhid", "h14q2", "h14q3")) %>%
    mutate(across(c("h14q2", "h14q3"), as.integer)) %>%
    mutate(have_one = h14q3 == 1 | h14q3 == 4 | h14q3 == 5) %>%
    select(-c(h14q3)) %>%
    pivot_wider(id_cols = hhid, names_from = h14q2, values_from = have_one) %>%
    select(c("hhid", `10`, `11`, `12`)) %>%
    rename(bike = `10`, motorbike = `11`, `motor_vehicle` = `12`) %>%
    mutate(country = (str_split(key, "_"))[[1]][[1]]) %>%
    mutate(year = (str_split(key, "_"))[[1]][[2]])
}
```
<hr> ### Plot
```{r warning=FALSE, message=FALSE, results=FALSE, eval=FALSE}
# Loop through the years for Uganda
  # Each year, make a plot with normalized scale
for (key in names(df_list)) {
  # THIS FIRST RUN OF plotVenn ONLY RETRIEVES THE $def OUTPUT, FOR RESCALING
  myV <- plotVenn(list(
    bike          = subset(df_list[[key]], bike)$hhid, 
    motorbike     = subset(df_list[[key]], motorbike)$hhid,
    motor_vehicle = subset(df_list[[key]], motor_vehicle)$hhid #, 
                             # COMMENT-OUT PREVIOUS COMMA TO REMOVE NO_TRANSPORT
#    no_transport  = subset(df_list[[key]], !motor_vehicle & !motorbike & !bike)$hhid 
                              # COMMENT-OUT PREVIOUS LINE TO REMOVE NO_TRANSPORT
  ), nCycles = 3000)$def
  
  # RESCALING
  nSets <- as.numeric(myV[2])
  a <- 3 + nSets
  b <- length(myV)
  n_hh <- length(df_list[[key]]$hhid)
  sNames <- myV[3:(a-1)]
  sSizes <- as.numeric(myV[a:b])
  sSizesNorm <- round(sSizes * 1000/n_hh)
  
  # PLOT
  myV3 <- createVennObj(nSets=nSets, sNames=sNames, sSizes=sSizesNorm)
  myV3 <- plotVenn(nVennObj = myV3, nCycles = 5000,
                   fontScale = 1, #systemShow = TRUE,
                   setColors=c("#00F", "#0F0", "#F00"), #, "#000"), 
                               # COMMENT-OUT FOURTH COLOR TO REMOVE NO_TRANSPORT
                   outFile=paste("./svg/", {{key}}, ".svg", sep=""))
}
```

``` {r include=FALSE eval=FALSE}

mean_nobs = mean(unlist(map(df_list, ~ length(.[[1]]))))

```

### Next Steps
- Try using "library(flexdashboard)" to:
    - Make plots flex to vertical alignment with narrower screens. (like normal html div columns)
    - Include a limited gapminder clone via plotly with just Albania and Uganda.
    - Add embedded scenes from Dollar Street: 25% median 75% quintile-income households side-by-side.
- Add a table of statistics

```{r include=FALSE}
# It was not long before the otherwise unremarkable Lazarat became a byword for quality in the coffee shops of Amsterdam. At peak production, the town was estimated to be turning out 900 tons of marijuana a year, with a street value of $6.1 billion. In 1999, Albania’s GDP was equivalent to just $3.4 billion.

# https://www.kaggle.com/jhossain/explore-the-gapminder-dataset-with-plotly-express
```